A point-level trend model for the North American Breeding Bird Survey that corrects for detectability

### 2024-04-04 article/article.tex
very small but nonzero amount of writing

\usepackage{setspace}
\onehalfspacing

@@

%\section{Next Analysis Steps}
%\subsection{Develop Model Code}
%Given Equation \ref{bbs_varprop}, the next steps would be to write this model in Stan. This can likely be done relatively quickly as the spatially explicit base model is available through the R package \textit{bbsBayes2} \citep{edwards_bbsbayes_2021}, and so this pre-existing model file can easily be modified to include the above effects and offset.

%\subsection{Test Model}

>>>>

\usepackage{setspace}
\doublespacing

@@

\subsection{Data Acquisition}

\subsection{Breeding Bird Survey Data}

\par We used the package \texttt{bbsBayes2} to download and process BBS data \citep{edwards_bbsbayes_2021}. 
For analysis with the route-level model, we followed the same data preparation steps as normal, in that data were downloaded from the USGS ScienceBase site, stratified based on a 1-degree by 1-degree block of latitude and longitude, prepared for modelling in Stan, and then modelled.
